---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# themeparks

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/themeparks)](https://CRAN.R-project.org/package=themeparks)
[![R-CMD-check](https://github.com/LucyMcGowan/themeparks/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/LucyMcGowan/themeparks/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of themeparks is to allow R users to access the themeparks.wiki API.

## Installation

You can install the development version of themeparks like so:

``` r
devtools::install_github("LucyMcGowan/themeparks")
```

## Example

You can access the available destinations using the `get_destinations` function:

```{r example}
library(themeparks)
get_destinations()
```

Once you have a destination in mind, you can find more information using the `get_entity` function. For example, if I want to pull all entity data for the Walt Disney World Resort, I can use the `slug` provided in the above dataset (or the `id`).

```{r}
get_entity("waltdisneyworldresort")
```
If you would like to all of the available parks, attractions, dining, and shows for a particular destination, you can use `get_entity_children`.

```{r}
get_entity_children("waltdisneyworldresort")
```

If you would like to extract live data for a particular attraction, you can use `get_entity_live_data`:

```{r}
get_entity_live_data("junglecruise")
```

You can also get all of the current wait time data for a particular destination, for example, for Walt Disney World:

```{r}
wdw_waits <- get_wait_times("waltdisneyworldresort")
wdw_waits[order(-wdw_waits$wait_time), ]
```

